Multimodal spatial availability: a singly-constrained measure of accessibility considering multiple modes

### 2024-02-07 Journal-manuscript/Journal-manuscript.tex
Version submitted to (journal) production

\caption{Accessibility\ values\ at\ each\ origin\ (i)\ per\ mode\ (m)\ (columns\ three\ to\ five)\ and\ aggregated\ per\ i\ (columns\ six\ and\ seven)\ for\ the\ synthetic\ example.}\\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{i}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{m}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{S}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{m}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{a}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{m}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{V}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{m}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedleft}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{a}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{V}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}} \\

\ascline{1.5pt}{666666}{1-7}\endfirsthead \caption[]{Accessibility\ values\ at\ each\ origin\ (i)\ per\ mode\ (m)\ (columns\ three\ to\ five)\ and\ aggregated\ per\ i\ (columns\ six\ and\ seven)\ for\ the\ synthetic\ example.}\\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{i}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{m}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{S}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{m}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{a}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{m}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{V}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}\textcolor[HTML]{000000}{\textsuperscript{\fontsize{11}{11}\selectfont{m}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedleft}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{a}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{V}}\textcolor[HTML]{000000}{\textsubscript{\fontsize{11}{11}\selectfont{i}}}} \\

@@

To close, in this work spatial availability considers competition by
allocating opportunities (the subject of the single-constraint) to modal
populations in zones based on zonal proportions. Opportunity congestion
can be seen on a continuum, but how it is to be considered within
accessibility research is an ongoing subject of exploration
{[}14,17,18{]}. It is in this context we present spatial availability
and its multimodal extension. While our focus was on a multiple modes,
this consideration is just one case of heterogeneous populations (i.e.,
travel by different modes). The multimodal method itself can easily
accommodate other forms of population or opportunity heterogeneity, for
example: variations in rich and poor, young and old, types of
opportunities. Like preceding accessibility measures, the potential
applications of spatial availability are as numerous as the potential
study contexts.

\hypertarget{author-contributions}{%
\section{Author contributions}\label{author-contributions}}

The authors confirm contribution to the paper as follows: study
conception and design: AS, JTO, JSL, AP.; data collection: AS, JTO,
JSL.; analysis and interpretation of results: AS, JTO, JSL, AP.; draft
manuscript preparation: AS, JSL, AP. All authors reviewed the results
and approved the final version of the manuscript.

>>>>

\caption{Accessibility\ values\ (S,\ a,\ V)\ at\ each\ origin\ (i)\ for\ the\ synthetic\ example.\ Displayed\ per\ mode\ (m)\ (columns\ three\ to\ five)\ and\ aggregated\ per\ i\ (columns\ six\ and\ seven).}\\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{i}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{m}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{S}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsuperscript{m}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{a}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsuperscript{m}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{V}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsuperscript{m}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedleft}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{a}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{V}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}} \\

\ascline{1.5pt}{666666}{1-7}\endfirsthead \caption[]{Accessibility\ values\ (S,\ a,\ V)\ at\ each\ origin\ (i)\ for\ the\ synthetic\ example.\ Displayed\ per\ mode\ (m)\ (columns\ three\ to\ five)\ and\ aggregated\ per\ i\ (columns\ six\ and\ seven).}\\

@@

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.88in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{i}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.41in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{m}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{S}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsuperscript{m}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{a}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsuperscript{m}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{V}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsuperscript{m}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\raggedleft}m{\dimexpr 0.58in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{a}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}} & \multicolumn{1}{>{\raggedleft}m{\dimexpr 1.05in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{V}}\textcolor[HTML]{000000}{\fontsize{11}{11}\selectfont{\textsubscript{i}}}} \\

@@

To close, in this work spatial availability considers competition by
allocating opportunities (the subject of the single-constraint) to modal
populations in zones based on zonal proportions. Opportunity congestion
can be seen on a continuum, but how it is to be considered within
accessibility research is an ongoing subject of exploration
{[}14,17,18{]}. It is in this context we present spatial availability
and its multimodal extension. While our focus was on a multiple modes,
this consideration is just one case of heterogeneous populations (i.e.,
travel by different modes). The multimodal method itself can easily
accommodate other forms of population or opportunity heterogeneity, for
example: variations in rich and poor, young and old, types of
opportunities. Similar to preceding accessibility measures, the
applications of spatial availability are as numerous as potential study
contexts. To encourage open and reproducible science, the manuscript and
all associated analysis is available within the lead author's
\href{https://github.com/soukhova/Multimodal-spatial-availability}{GitHub
repository}.
